---
title: "Section 4: Indexing, Data Wrangling, Plots - Assesment"
subtitle: 'HarvardX - PH125.1x, Data Science: R Basics'
author: "Rita Raher"
date: "05 Sep 2020"
output: 
  html_document:
    highlight: tango
    theme: cerulean
    toc: yes
    toc_depth: 4
    toc_float: yes
    keep_md: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question 1

Load the heights dataset from dslabs:

```{r setup}
library(dslabs)
data(heights)

```

Write an ifelse() statement that returns 1 if the sex is Female and 2 if the sex is Male.

What is the sum of the resulting vector?

```{r question1}
sum_up <-ifelse(heights$sex=="Female", 1, 2)
sum(sum_up)
```

## Question 2

Write an ifelse() statement that takes the height column and returns the height if it is greater than 72 inches and returns 0 otherwise.

What is the mean of the resulting vector?

```{r question2}

tall <- ifelse(heights$height >72, heights$height, 0)
mean(tall)


```

## Question 3

Write a function inches_to_ft that takes a number of inches x and returns the number of feet. One foot equals 12 inches.

What is inches_to_ft(144)?

```{r question3}

inches_to_ft <- function(x){
  feet <-x /12
  feet
  
}

inches_to_ft(144)

```
How many individuals in the heights dataset have a height less than 5 feet?

```{r question3a}

inches_to_ft <- function(x){
  feet <-x /12
  feet
}

heights_in_ft <- inches_to_ft(heights$height) 

summary(heights_in_ft <5)
```
## Question 4

Which of the following are TRUE?

```{r question4}

any(TRUE, TRUE, TRUE)
# true
any(TRUE, TRUE, FALSE)
# TRUE
any(TRUE, FALSE, FALSE)
# TRUE
any(FALSE, FALSE, FALSE)
# False
all(TRUE, TRUE, TRUE)
# TRUE
all(TRUE, TRUE, FALSE)
# False
all(TRUE, FALSE, FALSE)
# False
all(FALSE, FALSE, FALSE)
# False
```
## Question 5

Given an integer x, the factorial of x is called x! and is the product of all integers up to and including x. The factorial() function computes factorials in R. For example, factorial(4) returns 4! = 4 × 3 × 2 × 1 = 24.

```{r question5}
# define a vector of length m
m <- 10
f_n <- vector(length = m)

# make a vector of factorials
for(n in 1:m){
f_n[n] <- factorial(n)
}

# inspect f_n
f_n
```
